Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-06-10 Paper.Rmd
sending it to the danışman.

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 7,
                      echo = FALSE)
```

@@

-   mention moderating effects of product type for every variable

@@

@@

-   extend this later and try to connect to the methodology

@@

-   might explain why negative reviews arent that helpful for movies

@@

-   needs to be connected to the method

@@

Online Customer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective perspectives (writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@nelson1970] ; @liu2014; @ghose2006; @baek2012; @lee2016].

BestBuy is a very big electronics retailer and because of this the website offers a sizable number of OCR for search goods. Contrary to experience goods, search goods usually have more objectively quantifiable traits. For example, resolution or screen size of a TV, RAM or GPU of a Laptop, storage or battery lifetime of a Smart Phone. Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019]. Therefore, we collected search goods data from BestBuy.

@@

From IMDB reviews of 22 movies were collected as experience goods. In total 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never voted. To make sure that we are analyzing reviews that were actually read by people, we set a threshold for Total Reviews as five. In other words, we removed reviews that have less than 5 Total Votes [@choi2020; @baek2012]. At the very end, we were left with 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times.

It should be noted that in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names. All duplicates along with original reviews were removed because the reviews had different helpfulness ratios.

@@

As an outline, firstly the dependent variable is going to be introduced in a univariate manner and then independent variables are going to come into the picture both in univariate and bivariate way.

@@

Hong et al. (2014) [@hong2014; @sun2019] states that consumers likely to form homogeneous opinions about search goods. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is be enough to reveal the quality of a product. I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This is because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it.

-   you can elaborate a little bit more about how movies cant be evaluated objectively

@@

```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods.", fig.height=7}
p1 <- search_goods %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  labs(y = "Count", x = NULL)

@@

plots <-  p1 / p2

@@

```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods.", fig.height=7}
p1 <- movies_data %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count", x = NULL)

@@

-   you might add confidence interval for mean on plots.

@@

-   maybe add more framework for experience goods and no relationship

```{r Search-Length, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Number of the Words")

@@

plots <-  p1 / p1_log / p2 / p2_log

@@

```{r Experience-Length, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Number of the Words")

@@

1.  The first review date for a particular brand and model of a product (movie, phone, laptop, tv) was taken.
2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and model resulting an integer variable representing days.
3.  Bigger numbers represent more recent reviews.

@@

```{r Search-Freshness, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Freshness of Review")

@@

```{r Experience-Freshness, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Freshness of Review")

@@

Negative words were derived by using NRC Word-Emotion Association Lexicon @Mohammad13. A lexicon is basically a dictionary of words. These words might have similar emotions or sentiments. In this case, negative words lexicon was used in order to engineer this variable.

$$
Negative\ Word \% = \frac{Number\ of\ Matched\ Negative\ Word}{Total\ Words\ in\ Review} 
$$

@@

1.  Words in a review were tokenized.
2.  Tokenized words were matched with the words in the lexicon.
3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
4.  Logarithmic transformation was applied in order to scale the variable in a better way.

@@

On Figure \@ref(fig:Search-Neg) (B), non-linear relationship between perceived helpfulness and the proportion of negative words can be observed search goods. It should be kept in mind that as the proportion increases the sample size decreases. This might mean that any statistical test for non-linearity would have low power. On the other hand, somewhat weak negative linear relationship between perceived helpfulness and proportion of negative words can be seen for experience goods on Figure \@ref(fig:Experience-Neg) (B).

-   need citation here!

```{r Search-Neg, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

@@

```{r Experience-Neg, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

@@

@@

@@

-   needs sth from literature here as well

```{r Search-Pos, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

@@

```{r Experience-Pos, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

@@

>>>>

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8,
                      fig.height = 4,
                      echo = FALSE)
```

@@

@@

The classification of Experience and Search goods plays a moderating role in the literature [@mudambi2010; @sun2019; @baek2012; @lee2016]. Some of these studies showed that Review Length has a greater effects for search products than experience products [@mudambi2010; @baek2012; @lee2016]. These findings suggest that search goods can be evaluated in a more objective way than experience goods. The moderating effect of product type on Review Extremity, on the contrary, is disputable. Mudambi (2010) @mudambi2010 showed that moderate reviews are more helpful for experience products than search products. Baek (2012) @baek2012 and Lee (2016) @lee2016 had the opposite results which indicated that more extreme reviews (negative or positive) is more helpful more search goods than experience goods.

@@

-   could be extended later

@@

-   might explain that goods within the same group can show different characteristics

@@

-   should be extended a little bit more

@@

Online Customer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].

BestBuy is a very big electronics retailer and because of this the website offers a sizable number of OCR for search goods. Contrary to experience goods, search goods usually have more objectively quantifiable traits. For example, resolution or screen size of a TV, RAM or GPU of a Laptop, storage or battery lifetime of a Smart Phone. Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019]. Therefore, search goods data was collected from BestBuy.

@@

From IMDB reviews of 22 movies were collected as experience goods. In total 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never voted. To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five. In other words, reviews that had less than 5 Total Votes were removed from the analysis data[@choi2020; @baek2012]. At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times. Most of the search product reviews aren't getting voted and even maybe they aren't getting read at all. This might support the idea that people form more homogeneous opinions about search goods @hong2014. Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information. On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times. This might be because people form heterogeneous opinions about experience goods @hong2014.

As a data cleaning note, in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names. All duplicates along with original reviews were removed because the reviews had different helpfulness ratios.

@@

In this section there will be univariate visualizations of all variables and bivariate visualizations of independent variables against the dependent variable.

-   elaborate more on the importance of EDA here

@@

Hong et al. (2014) [@hong2014; @sun2019] states that consumers likely to form homogeneous opinions about search goods. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods."}
p1 <- search_goods %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  labs(y = "Count", x = "Review Rating")

@@

plots <-  p1 + p2

@@

```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods."}
p1 <- movies_data %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count", x = "Review Rating")

@@

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Number of the Words")

@@

plots <-  (p1 + p1_log) / (p2 + p2_log)

@@

```{r Experience-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Number of the Words")

@@

1.  The first review date for a particular brand and model of a product (Movie, Phone, Laptop, TV) was taken.
2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and model resulting an integer variable representing days.
3.  Bigger numbers represent more recent reviews.

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Freshness of Review")

@@

```{r Experience-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Freshness of Review")

@@

Negative words were derived by using NRC Word-Emotion Association Lexicon @Mohammad13. A lexicon is basically a dictionary of words. These words might have similar emotions or sentiments. In this case, negative words lexicon was used in order to engineer this variable. A sample of negative words from the lexicon can be observed below.

*"caricature, superstition, compost, misconception, grief, violation, scrub, omen, erratic, porcupine"*

$$
Negative\ Word \% = \frac{Number\ of\ Matched\ Negative\ Word}{Total\ Words\ in\ the\ Review} 
$$

@@

1.  Words in a review were tokenized.
2.  Tokenized words were matched with the words in the lexicon.
3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
4.  Logarithmic transformation was applied in order to scale the variable in a more normalized way.

@@

On Figure \@ref(fig:Search-Neg) (B), non-linear relationship between perceived helpfulness and the proportion of negative words can be observed for search goods. This might suggest that too much negative information might fall into slander rather than informing the customer about the potential risks of the product. On the other hand, somewhat weak negative linear relationship between perceived helpfulness and proportion of negative words can be seen for experience goods on Figure \@ref(fig:Experience-Neg) (B).

```{r Search-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Negative Words)")

@@

```{r Experience-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Negative Words)")

@@

$$
Positive\ Word \% = \frac{Number\ of\ Matched\ Positive\ Word}{Total\ Words\ in\ the\ Review} 
$$

@@

*A sample of positive words from EmoLex:*

*"covenant, jovial, score, foundation, affirmation, reliable, mending, garden, luxurious, wit"*

@@

```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

@@

```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

@@

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\
--- --- --- ---

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

--- --- --- ---

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

--- --- --- ---
